econ

### 2024-01-07 abc.qmd
delabc

---
title: "econ"
#format: 
#  html:
#    css: "https://kineticgraphs.org/css/kg.0.2.7.css"
#    include-in-body:
#          - text: |
#              <script src="https://kineticgraphs.org/js/kg.0.2.7.js"></script>
---

<head>
      <script src="https://kineticgraphs.org/js/kg.0.2.7.js"></script>
      <link rel="stylesheet" href="https://kineticgraphs.org/css/kg.0.2.7.css">
</head>

<div class="kg-container">
schema: EconSchema
layout:
  OneGraph:
    graph:
      xAxis: 
        title: "Good 1"
      yAxis: 
        title: "Good 2"
      objects: 
      - EconBudgetLine:
          p1: 1
          p2: 2
          m: 8
          label: {text: M, location: 0.9}
</div>

<html>
  <head>
    <script src="https://cdn.jsdelivr.net/pyodide/v0.24.1/full/pyodide.js"></script>
  </head>

@@

      async function evaluatePython() {
        let pyodide = await pyodideReadyPromise;
        try {
          let output = pyodide.runPython(code.value);
          addToOutput(output);
        } catch (err) {
          addToOutput(err);
        }
      }
    </script>
  </body>
</html>

>>>>

---
title: "econ"
#format: 
#  html:
#    css: "https://kineticgraphs.org/css/kg.0.2.7.css"
#    include-in-body:
#          - text: |
#              <script src="https://kineticgraphs.org/js/kg.0.2.7.js"></script>
---
<head>
      <link rel="stylesheet" href="https://kineticgraphs.org/css/kg.0.2.7.css">
      <script src="https://kineticgraphs.org/js/kg.0.2.7.js"></script>
</head>

<body>
<div class="kg-container">
schema: EconSchema
  layout:
    OneGraph:
      graph:
        xAxis: 
          title: "Good 1"
        yAxis: 
          title: "Good 2"
        objects: 
        - EconBudgetLine:
            p1: 1
            p2: 2
            m: 8
            label: {text: M, location: 0.9}
</div>
</body>

```{r, eval=T}
knitr::knit_exit()
```

<head>
  <script src="https://cdn.jsdelivr.net/pyodide/v0.24.1/full/pyodide.js"></script>
</head>

@@

    async function evaluatePython() {
      let pyodide = await pyodideReadyPromise;
      try {
        let output = pyodide.runPython(code.value);
        addToOutput(output);
      } catch (err) {
        addToOutput(err);
      }
    }
  </script>
</body>
